---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "Rebecca D. Calcott"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "rdcalcott@gmail.com"
  - name          : "Elliot T. Berkman"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Regensburg"
  - id            : "2"
    institution   : "University of Oregon"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library(papaja)
library(bibtex)
library(itrackR)
library(edfR)
library(dplyr)
library(dtplyr)
library(ggplot2)
library(lme4)
library(haven)
library(lmerTest)
library(effects)
library(psych)
library(knitr)
library(sjPlot)
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```

```{r data setup, include=FALSE}
# Hard-coded file pathways and experiment numbers (data paths must correspond to expNums)
genericDataPath <- '~/Dropbox/Studies/Dissertation/output/Study' 
expNums <- c(1,2,4) #list only those with eye data
noEyeDataExp <- 3

# Establish absolute performance cutoffs for inclusion
excludeRTmax <- 2000
excludeRTmin <- 100
excludeRTmaxSDs <- 3
excludeSaccLatency <- 750
targetHitThresh <- .75 # below this threshold, exclude subjects for not fixating the target on enough trials.

# function to load, re-name, and merge data
loadData <- function(expNum, genericDataPath) {
  assign('dataPath', paste(genericDataPath, expNum, '/', sep=''))
  
  load(paste(dataPath, 'cleanDataBehAnalyses.Rda', sep='')) 
  load(paste(dataPath, 'eyetrackingData_byTrial.Rda', sep='')) 
  load(paste(dataPath, 'blinks.Rda', sep='')) 
  
  allData <- merge(cleanData_behAnalyses, blinks, by='ID', all.x=FALSE, all.y=FALSE)
  allData <- merge(allData, allEyes, by=c('ID','Block','Set','Trial'))
  
  assign(paste('allData',expNum, sep=''), allData)
}

#function to load data for experiments without eyetracking data
loadDataNoEyeData <- function(expNum, genericDataPath) {
  assign('dataPath', paste(genericDataPath, expNum, '/', sep=''))
  
  load(paste(dataPath, 'cleanDataBehAnalyses.Rda', sep='')) 
  
  assign(paste('allData',expNum, sep=''), cleanData_behAnalyses)
}

list <- sapply(expNums, loadData, genericDataPath=genericDataPath, USE.NAMES=TRUE)
list2env(setNames(list, paste('allData',expNums,sep='')), envir=.GlobalEnv)

#load data for experiment with no eye data:
load(paste(genericDataPath, noEyeDataExp, '/cleanDataBehAnalyses.Rda', sep=''))
assign(paste('allData',noEyeDataExp, sep=''), cleanData_behAnalyses)

```

Effective goal-driven behavior requires not only the ability to maintain task-relevant representations in working memory (WM), but also to update these representations when the situation requires. For example, imagine an individual who is searching for her friend in a crowd with the knowledge that this friend is wearing a red hat. Once she has located her friend, she learns that another friend is wearing a blue coat, and so her attentional template in working memory must be updated to blue. There is a high degree of variability in the ease with which we can update these WM representations. Whereas some states and traits promote excessive stability, resulting in perseveration on no-longer relevant representations, others give rise to excessive flexibility, which may result in task-irrelevant representations gaining access to WM. [Interestingly, many of these traits have been linked with dopamine...]. Additionally, task-specific characteristics, such as the presence of potentially distracting stimuli, determine the processes required for effective WM updating, and thus the effectiveness with which one can update WM representations and shield these new representations from distraction. From our example, how will the search for a blue coat be impacted by the presence of many red hats in the crowd, when our subject had been previously searching for a red hat? The present research explores how the presence of interference affects the ability to update WM representations, and its relationship with spontaneous eye blink rate (EBR), an index of striatal DA, with the goal of determineing the conditions under which striatal DA is most relevant to updating ability.

## Working memory updating
Across range of tasks (e.g. task switching, attentional set-shifting), the need to update WM representations consistently incurs a performance cost in both speed and accuracy [CITE]. However, not all WM updates are equivalently costly - specific task factors modulate the degree to which performance suffers during a switch.
First, switching is more costly when participants must ignore a previously-relevant stimulus that is presented at the same time as the target [@RogersMonsell_1995], as would be the case when having to attend blue and ignore red after previousy attending red. Furthermore, this inhibition of no-longer-relevant representations appears to be automatically triggered during WM updating [@MayrKeele_2000], indicating that updating involves not only the activation of the newly-relevant representations, but also active inhibition of those that are no longer relevant. The upshot of this inhibition is that switching back to a representation that was previously inhibited incurs a cost because individuals must overcome the inhibition to re-activate the particular representation. This process of actively disengaging from no-longer relevant representations plays a key role in a recent model of cognitive control more generally, and may explain variability in WM capacity, or the ability to hold items in WM [@ShipsteadEtAl_2016]. Thus, in situations in which individuals must update WM by switching the same set of representations (i.e. familiar stimuli), costs may arise both via perseveration on an old representation, as well as the need to overcome inhibition of a previously-irrelevant representation.
An additional moderating factor is the predictability of the switch. When the need to update WM is completely predictable, performance improves to baseline levels only one trial following the switch. On the other hand, when switches are unpredictable, performance improvements are more gradual, and asymptote to baseline levels only after several trials following the switch [@MonsellEtAl_2003]. An open question concerns how switching between familiar stimuli affects the number of trials required to return to baseline performance following an unpredictable switch.

## The role of striatal dopamine (DA) in working memory updating
Computational models highlight the role of striatal DA in WM updating processes [@HazyEtAl_2007; @FrankEtAl_2001]. Whereas the PFC [not storage, but___], the dorsal striatum acts as a gate, controlling which representations gain access to the PFC based on which representations have predicted positive outcomes in the past [@HazyEtAl_2007]. This gate is regulated by two DA receptor subtypes: D1- and D2-Type. Phasic DA signals [from ____] activate D1 receptors, which has the downstream effect of lifting inhibition of PFC, and triggering updating of WM representations. At low striatal DA levels, D2 receptors are more active, which has the effect of inhibiting gating. Thus, whether or not WM updating occurs depends on the relative activation of the D1 and D2 pathways, which is DA-dependent.
In addition to phasic signals, tonic DA level in striatum are also theorized to influence the relative ease of WM updating, primarily via its effects on the D2 pathway [@MaiaFrank_2011]. When tonic DA is high, the D2 pathway is less active and thus the threshold required for a phasic DA signal to trigger updating is lowered and thus WM updating should be facilitated. On the other hand, when tonic DA is low, the D2 pathway will be more active, resulting in greater inhibition of gating and thus an increased threshold for WM udpdating.
Some empirical evidence supports this link between D2 pathway activation and WM updating. Higher D2 receptor density in ___ predicted improved reversal learning, which requires the ability to update WM representations [@GromanEtAl_2014]. Furthermore, a D2 receptor agnonist improved performance in human subjects with low tonic DA [@vanHolsteinEtAl_2011]. [find more references].
On the other hand, there are also some inconsistent findings with respect to the relationship between tonic DA and WM updating. [Give examples]. An open question is whether tonic DA levels have different implications for WM updating depending on task properties, and in particular, whether WM updating also requires inhibition of potentially interfering familiar stimuli.

## Spontaneous eye blink rate (EBR) as an index of striatal DA function
The above question has been addressed by studies using spontaneous eye blink rate (EBR), which is hypothesized to be an index of tonic striatal DA tone [@JongkeesColzato_2016]. The physiological link between EBR and DA function is not yet fully understood; however EBR is predictive of D2-type receptor density and availability [@GromanEtAl_2014] and is often interpreted as an index of tonic striatal DA levels [@JongkeesColzato_2016]. [more evidence on EBR here... citations from Cools lab!].
There are, however, inconsistent findings with respect to the relationship between DA and EBR. A recent pilot study [@SescousseEtAl_2017] used positron emission tomography (PET) to assess the relationship between striatal DA synthesis capacity and EBR. If EBR is indeed predictive of greater striatal DA levels, we may expect that higher EBR would predict greater DA synthesis capacity; however the study found no significant relationship and if anything, the trend was towards a negative relationship [@SescousseEtAl_2017]. [cite other study cited by Sescousse et al]. Thus, the relationship between EBR and DA is likely to be nuanced and may not map well onto the amount of DA that is present in the striatum.
In spite of these inconsistencies about the precise relationship between EBR and striatal DA, EBR does consistently predict WM updating ability; however the direction of this relationship depends on the specific task used. @DreisbachEtAl_2005 used an attention set-shifting task with two updating conditions: In the Perseveration condition, updating involved shifting attention to an unfamiliar target color and ignoring a previously-relevant colour, whereas in the Learned Irrelevance condition, participants updated by shifting attention to a previously-ignored colour and ignoring a novel colour. Higher EBR predicted faster updating in the Perseveration condition, but slower updating in the Learned Irrelevance condition, and this finding has since been replicated [@MuellerEtAl_2007]. This work underscores the importance of specific task factors, such as whether the new target and distractor are novel or familiar, and their previous role in the task. However, it is not yet clear which factors are driving the results. On the one hand, it is possible that higher EBR predicts improved ability to inhibit no-longer relevant representations, which would improve performance in the Perseveration condition but may harm performance in the Learned Irrelevance condition, because it may be more difficult to overcome the stronger backwards inhibition to activate a particular task set. On the other hand, it is also possible that high EBR predicts a novelty bias, making it easier to shift attention towards novel stimuli, but also less able to ignore novel stimuli when they are not task-relevant. [Link with computational models and DA -> what could this mean?]
In our own pilot study (*N*=61), participants performed a similar set-shifting task, which cued participants to shift their attention among 3 potential colors, all of which were present, either as distractors or target, on all trials. Thus, at each switch point, participants had to update their attentional set to attend a color that was previously a distractor and ignore a colour that was previously a target. Under these conditions, higher EBR predicted slower updating (*r*=.28, *p*=.03). Because there were no novel targets in this task, and in light of previous findings showing that higher EBR predicts less perseveration [@DreisbachEtAl_2005; @MuellerEtAl_2007], this finding suggested that perhaps participants with higher EBR had more difficulty overcoming inhibition of previously-irrelevant representations, potentially because of stronger inhibition of irrelevant information. Other work using the Stroop task has indeed shown that participants with higher EBR were better at ignoring irrelevant stimulus dimensions [@ZhangEtAl_2015]. Thus, it is possible that participants with high EBR also inhibit irrelevant task sets more strongly, which makes it more difficult to overcome to attend a target that has previously been a distractor. If EBR does indeed reflect striatal DA levels, we might expect that if this ___ was removed and things were equal, that higher EBR would predict improved updating, by lowering the threshold required to gate new task representations into the PFC.

## The present studies
Using an attention shifting task, the present studies will explore how the effectiveness and time scale of WM updating varies, depending on whether individuals must inhibit interference from previously-relevant task sets. Additionally, we will compare the relationship between EBR and WM updating across these different task contexts with the aim of .
In a series of 4 experiements, participants completed a cued attentional shifting task consisting of two updating conditions: Perseveration-Inhibition and Pure Updating. In the Perseveration-Inhibition condition, updating involved shifting the focus of attention away from a current target colour to instead attend what was previously the distractor. Thus, both target and distractor were familiar to subjects, and switch costs may be, in part, attributable to both perseveration on the old target color as well as needing to overcome backwards inhibition of the new target. In the Pure Updating condition, updating involved shifting attention to a novel target and ignoring a novel distractor, and thus switch costs cannot be attributable to interference from a previous attentional set.
Based on the results of our pilot study, we expected that in the Perseveration-Inhibition condition, higher EBR would again predict slower WM updating. Based on the idea of EBR as an index of striatal DA levels, we additionally hypothesized that higher EBR would predict faster WM updating in the Pure Updating condition, because higher DA levels should bias the fronto-striatal network towards updating by lowering the threshold required for a phasic DA signal to trigger updating [@MaiaFrank_2011].
It is important to note, however, that although there is much evidence for a link between striatal DA and EBR [e.g., @JongkeesColzato_2016], the specific nature of this relationship is still unknown, and as outlined above, is likely to be more complicated than a straightforward index of striatal DA levels. Thus, for the present paper, we are using EBR to determine the conditions under which striatal DA function is most relevant to WM updating; however we will not be able to draw any directional conclusions about the relationship between striatal DA tone and WM updating.
The present studies also had the exploratory aim of determining the temporal dynamics of updating (Perseveration-Inhibition vs. Pure Updating), by examining performance as a function of the number of trials from an update, and additionally how these temporal measures are related to EBR. For the sake of transparency, we note that we did not initially intend to examine the data in this way; however the data showed that performance in this task did not immediately reach baseline levels one trial following the switch, but rather asymptoted more slowly over the course of several trials, and this is consistent with other work in which the timing of WM updating is unpredictable [@MonsellEtAl_2003].
An additional advantage of the present study is that participants' eye movements were tracked, which made it possible to examine the eye movements underlying performance differences across conditions and individuals. 

# Experiment 1
Experiment 1 addresses how the ease and time scale of WM updating varies depending on whether the task requires inhibition of a prior attentional set, and whether these measures are related to EBR.

## Methods
### Participants
A power analysis based on our pilot study indicated that data from 100 participants were necessary in order to obtain statistical power of 0.8 with an alpha of .05 for the relationship between EBR and switch cost (*r*=.28). Thus, 123 students at the university of Oregon participated in this experiment for partial course credit. Eligible participants were between 18-30 years old and reported having normal or corrected-to-normal color vision. Data from 13 participants were excluded prior to analyses because of task presentation failure (2), participant withdrawal or lack of time to finish task (5), inability to track eye (1), file corruption (1), and not meeting the eligibility criteria (4). The remaining 110 participants had a mean age of [insert] and included [insert] females, [insert] males, and [insert] individual who did not report being male or female. All procedures were approved by the Committee for the Protection of Human Subjects at the University of Oregon.
### Material

### Procedure

### Data analysis


## Results

## Discussion

# Experiment 2
## Methods

### Participants

### Material

### Procedure

### Data analysis


## Results

## Discussion

# Experiment 3
## Methods


### Participants

### Material

### Procedure

### Data analysis


## Results

## Discussion

# Experiment 4
## Methods


### Participants

### Material

### Procedure

### Data analysis


## Results

## Discussion

# General Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\endgroup
